%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% cv-friggeri-x 1.0 (01/01/2016)
% XeLaTeX Template
%
% Based on:
% Friggeri Resume/CV
% Version 1.2 (3/5/15)
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
% 
% Modified by:
% Nadorrano
% https://github.com/Nadorrano/cv-friggeri-x
%
% License:
% MIT
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography,
% if used, needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,nocolors]{friggeri-cv}
% Add `a4paper` to set a4 paper size
% Add `nocolors` to remove colors from the document
% Add `lightheader` to change the dark background of the header to white

\usepackage{marvosym} % needed to print glyphs for email, cell phone etc.
\usepackage{graphicx}
\usepackage{hyperref}
\addbibresource{bibliography.bib} % Specify the bibliography file to include publications
\begin{document}

\header{Bianca Eugenia }{Sozzi}{Android Software Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
\pin \hfill Anna-Mettbach-Str. 19
35394 Gießen
Germany\vspace{0.5em}
{\Large\textcolor{gray}{\Mobilefone}} \hfill +49 (177) 543 1281
\hfill \href{mailto:biancasozzi@gmail.com}{\scalebox{0.9}[1]{biancasozzi@gmail.com}}\vspace{0.75em}
\llogo \hfill \href{https://www.linkedin.com/in/bianca-eugenia-sozzi}{bianca-eugenia-sozzi}\vspace{2em}
~
\section{languages}
\textbf{English} \hfill Professional~
\textbf{Spanish} \hfill Native speaker~
\textbf{German} \hfill Intermediate (B1)~\vspace{2em}
\section{skills}
\textbf{Mentoring} \hfill \filleddot \filleddot \filleddot \filleddot \emptydot
\textbf{Agile} \hfill \filleddot \filleddot \filleddot \filleddot \filleddot
\textbf{Leadership} \hfill \filleddot \filleddot \filleddot \emptydot \emptydot
\textbf{Android} \hfill \filleddot \filleddot \filleddot \emptydot \emptydot
\textbf{Kotlin} \hfill \filleddot \filleddot \filleddot \emptydot \emptydot
\textbf{Java} \hfill \filleddot \filleddot \filleddot \emptydot \emptydot
\textbf{JetpackCompose} \hfill \filleddot \filleddot \emptydot \emptydot \emptydot
\textbf{AWS} \hfill \filleddot \filleddot \emptydot \emptydot \emptydot
\textbf{Python} \hfill \filleddot \filleddot \emptydot \emptydot \emptydot
\end{aside}
%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\section{summary}
\vspace{1em}
\\
6+ years of experience building scalable, high-impact applications across Android and backend systems. I’ve developed Android apps using Kotlin, Java, Jetpack Compose, MVVM, and Clean Architecture, while also contributing as a backend engineer using Python and Java to design robust APIs and services. I take pride in delivering reliable solutions that improve user experience and system performance, and I’m equally passionate about mentoring teammates and helping them grow.
\vspace{0.5em}
%------------------------------------------------

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entryexperience
{Sep 2024}
{Mar 2025}
{Geopagos - Android Software Engineer}
{Argentina · Remote}
{
• Developed an app utilizing the product's SDK for regression tests.\\
• Contributed to the development of team-owned SDKs at Geopagos.\\
• Supported white-label integrations where SDKs reached millions of end-users across client apps for payment processing.
}
{
  Kotlin · Kotlin Coroutines · Model-view-viewmodel (MVVM) · MVI · SOLID Design Principles · Clean Architecture · Koin · Retrofit
}

%------------------------------------------------

\entryexperience
{Jan 2022}
{May 2024}
{Eyeo - Android Software Engineer}
{Germany · Remote}
{
• Led key initiatives in the development of Samsung Content Blockers, resulting in a smoother and more privacy-focused browsing experience for millions of users via the Play Store.
\\
• Took ownership of major features in Adblock Browser, driving improvements in ad filtering and privacy protections, and helping grow the app’s active user base.
\\
• Acted as mentor to a Junior Android Developer, providing code reviews, architectural guidance, and onboarding support.
}
{
  Architectural Patterns · Kotlin · Java · Jetpack Compose · Kotlin Coroutines · Model-View-ViewModel (MVVM) · Hilt
}

%------------------------------------------------

\entryexperience
{Nov 2019}
{Dec 2021}
{Klarna - Java Software Engineer}
{Giessen, Hesse, Germany · Hybrid}
{
  • Provided personalized mentorship and guidance to colleagues who were new to Python, helping them graspfundamental concepts and navigate their initial coding projects with confidence
  \\
  • Integrated one of our risk services into AWS
  \\
  • Further developed the backend application using Java/Spring
}
{ 
  Architectural Patterns · Spring Boot  · Java · Python · Amazon Web Services (AWS) · Performance Testing · Sentry · Datadog
}

%------------------------------------------------

\entryexperience
{Aug 2018}
{Aug 2019}
{Eventbrite - Python Software Engineer}
{Provincia de Mendoza, Argentina}
{
  • Developed and maintained scalable APIs using Python and Django, improving system performance and user experience.

  • Worked with SQL databases to optimize data storage and retrieval processes.

  • Collaborated with cross-functional teams (product, design, QA) to deliver features in an agile, sprint-based environment.

  • Contributed to enhancing platform functionality by identifying and implementing backend improvements.
}
{
  Architectural Patterns · Python · Django · Unit Testing · Agile Methodologies · SQL
}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--2018}
{Engineer’s Degree {\normalfont Systems Engineering}}
{Universidad Tecnológica Nacional, Argentina}
{Graduated with a focus on Object Oriented Programming (OOP) and project management.}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{projects}
\begin{entrylist}
\entryproject
{Nov 2022}
{May 2024}
{Adblock Browser}
{eyeo GmbH}
{
  The Adblock Browser project focuses on delivering a fast, privacy-centric web
  browsing experience by integrating advanced ad-filtering technologies to eliminate
  unwanted content and enhance user security.
}
{https://play.google.com/store/apps/details?id=org.adblockplus.browser&pli=1}

\entryproject
{Jan 2022}
{Nov 2022}
{Content Blockers for Samsung Internet}
{eyeo GmbH}
{
  Content Blockers for Samsung Internet leverage their trusted Adblock Plus engine to give users a fast, private, and clean browsing experience. They integrate seamlessly with Samsung’s browser via official extension API, offer customizable filtering, and support sustainable web models through Acceptable Ads.
}
{https://play.google.com/store/apps/details?id=org.adblockplus.adblockplussbrowser}

\end{entrylist} 
\section{interests}

\textbf{professional:} Android development, Clean Architecture, Kotlin Multiplatform, Jetpack Compose, modular app design, RESTful API integration, dependency injection, scalable architecture, backend development (Java/Kotlin), testing and automation, SDK integration \\
\textbf{personal:} traveling, remote work, problem-solving, exploring new cultures, parenting (BLW), TV Series, Music, Reading
 
\end{document}
